---
title: "Week4 HW"
author: "Rie"
date: "4/25/2019"
output: 
  html_document: 
    keep_md: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

###4E1 In the model definition below, which line is the likelyhood?
y1

###4E2 In the model definition just above, how many parameters are in the post distribution?
2, mu and sigma

###4E3 Using the model definition above, write down the appropriate form of Bayes' theorem include the proper likelihood and priors.


###4E4 In the model definition below, which line is the linear model?
mu = alpha + beta*xi

###4E5 In the model definition above, how many parameters are in the posterior distribution?
3, alpha and beta, sigma



###4M1 For the model definition below, simulate observed heights from the prior (not the posterior)

```{r HW4M1}
library(rethinking)
data("Howell1")
d <- Howell1
d2 <- d[d$age>=18,]
head(d2)
sample_mu <- rnorm(1e4,178, 20) #1000 samples, average178, sd 20
head(sample_mu)
sample_sigma <- runif(1e4, 0, 50)
prior_h <- rnorm(1e1, sample_mu, sample_sigma)
dens(prior_h)
```
###4M2 Translate the model just above into a quap formula
```{r HW4M2}
flist <- alist(
  height <- dnorm(mu , sigma),
  mu ~ dnorm(178, 20),
  sigma ~ dunif(0,50)
)
m4.1 <- quap(flist , data=d2)
precis(m4.1)
```

###4M3 Translate the quap model formula below into a mathematical model definition

yi ~ Normal(mu, sigma) 
mu-i = alph + beta*x
alpha ~ Normal(0, 50)
beta ~uniform (0, 10)
sigma ~ uniform(-0, 50)

